### 2019-02-13 2-Chapters/Conclusion/conclusion.tex
Ok for tex root
Still fighting against my template...
Okay for chapters and parts

%!TEX root = ../thesis.tex

% First chapter begins here
\chapter*{General Conclusion and Perspectives}
\addcontentsline{toc}{chapter}{General Conclusion}
%\minitoc
\label{chapter:conclusion}
% Write miniTOC just after the title
\graphicspath{{2-Chapters/6-Chapter/Images/}}

In this PhD thesis, blabla.

@@

\section*{Perspectives}
We present in the following the possible areas of future studies

\subsubsection*{Blabla}
\begin{itemize}
\item Blabla
\end{itemize}

>>>>

%!TEX root = ../PhD_thesis__Lilian_Besson

% First chapter begins here
\chapter{General Conclusion and Perspectives}
% \addcontentsline{toc}{chapter}{General Conclusion}
\label{chapter:conclusion}
%\minitoc

Abstract for Conclusion.

% Write miniTOC just after the title
\graphicspath{{2-Chapters/6-Chapter/Images/}}

\section{General Conclusion}
In this PhD thesis, blabla.

@@

\section{Perspectives}
We present in the following the possible areas of future studies.

\section{Personal Summary}

I would like to highlight that from a personal point of view, this thesis was awesome blabla.

J'aimerai conclure en dédicaçant cette thèse à mes deux frères, qui ont été ma plus grande source d'inspiration depuis mon plus jeune âge ; ainsi qu'à la mémoire de XXX XXX qui nous manquera cruellement.
\textcolor{white}{Je souhaite aussi remercier une fois encore mes amis et amies les plus proches, Hélène, Pierre, Lola, Sélim, Angèle}
